Bioverse: Origins of Life

### 2024-07-13 src/tex/ms.tex
rewrite powergrid results

\subsubsection{Statistical power for a transit survey and sensitivity on astrophysical parameters}\label{sec:results-powergrid}
We now investigate the sensitivity of the achieved statistical power of our default transit survey to the a priori unconstrained threshold \gls{NUV} flux $F_\mathrm{NUV, min}$ and the abiogenesis rate $f_\mathrm{life}$.
Figure~\ref{fig:powergrid} shows the statistical power as a function of these parameters for a sample size of $N=\var{N_nautilus}$.
Values of $F_\mathrm{NUV, min}$ that lie between the extrema of the inferred maximum \gls{NUV} flux increase the achieved statistical power of the survey, as in this case the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis.
The same is true for the abiogenesis rate $f_\mathrm{life}$, where higher values increase the evidence for $H_1$.

@@

%We stress that a future observer will likely be able to leverage standard frequentist testing methods which may be more likely to yield conclusive results (whether in favor or in disfavor of $H_1$).
%For instance, it would make sense when presented with a sample of planets with various values of $F_{\mathrm{NUV}}$ and for which biosigature detection is attempted to categorize them into two classes: those for which a biosignature is detected, and those for which this is not the case.
%Then, the distribution of $F_{\mathrm{NUV}}$ in each of those categories is compared under the null hypothesis that they are the same.
%In this case, a non-parametric test could be preferred, such as a two-sample Kolmogorov-Smirnov test or perhaps a Mann-Whitney $U$ test.
% Is this what you end up looking at using BIOVERSE ? If so, then that should flow nicely with the rest.

\subsection{Constraining power for the origins of life as a function of biosignature location} % corresponds to conclusion points 2, 5
\todo[inline]{How does the location of biosignature detections impact the credibility of OOL scenarios?}
It comes to no surprise that the success rate of such a test is sensitive to the sample size of the survey and to the occurrence of life on temperate exoplanets.
As we have shown, the statistical power of this test also depends on the distribution of past \gls{NUV} fluxes in the sample and on the required threshold flux.
Optimizing the survey to sample a wide range of NUV flux values, particularly at the extremes, can enhance the likelihood of obtaining strong evidence for or against the hypothesis.
Intermediate values of the threshold \gls{NUV} flux are more likely to yield strong evidence than extreme values, as the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis in this case while still being sufficiently populated.
The required threshold flux is, of course, a priori unknown and we cannot influence it.
If, however, better theoretical predictions for the required \gls{NUV} flux for abiogenesis become available, the survey strategy can be further optimized, for instance by targeting planets that are estimated to have received a \gls{NUV} flux slightly below and above this threshold.

@@

\subsection{Contextual support for potential biosignature detections} % corresponds to ... which conclusion?
\todo[inline]{discuss how planetary context may impact credibility of tentative biosignature detections (e.g., if there is a good fit with a predicted OOL pattern; or the opposite: the planetary context does not fit well to any OOL scenarios)}
The predicted interplay of \gls{NUV} flux and \gls{HZ} occupancy in enabling abiogenesis via the cyanosulfidic scenario could in principle be used to add or remove credibility from a tentative biosignature detection.
For example, with a strong believe that this scenario is the only viable one for the origins of life, a biosignature detection on a planet orbiting a strongly UV-radiating star may add credibility to the detection.
Conversely, a biosignature detection on a planet estimated to have received very little UV~radiation would increase the likelihood of a false positive detection.
On the other hand, should the detection in the latter case be confirmed, it could be used to falsify the UV~hypothesis.

>>>>

\subsubsection{Statistical power for a transit survey and sensitivity on astrophysical parameters}\label{sec:results-powergrid}
We now investigate the sensitivity of the achieved statistical power of our default transit survey to the a priori unconstrained threshold \gls{NUV} flux $F_\mathrm{NUV, min}$ and the abiogenesis rate $f_\mathrm{life}$.
Figure~\ref{fig:powergrid} shows the statistical power as a function of these parameters for a sample size of $N=\var{N_nautilus}$.
Values of $F_\mathrm{NUV, min}$ that lie between the extrema of the inferred maximum \gls{NUV} flux increase the achieved statistical power of the survey, as in this case the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis.
Furthermore, a higher abiogenesis rate $f_\mathrm{life}$ increases the evidence for $H_1$.

Notably, the sensitivity of the M~dwarf sample extends into the low \gls{NUV} flux end due to the broader distribution of maximum past \gls{NUV} fluxes in this sample.
Here, the FGK sample is less sensitive.
The only parameter space region with statistical power above \SI{90}{\percent} lies at abiogenesis rates $f_\mathrm{life} > 0.9$ and threshold \gls{NUV} fluxes of $\sim \SIrange{30}{70}{\erg\per\second\per\centi\meter\squared}$.

@@

%We stress that a future observer will likely be able to leverage standard frequentist testing methods which may be more likely to yield conclusive results (whether in favor or in disfavor of $H_1$).
%For instance, it would make sense when presented with a sample of planets with various values of $F_{\mathrm{NUV}}$ and for which biosigature detection is attempted to categorize them into two classes: those for which a biosignature is detected, and those for which this is not the case.
%Then, the distribution of $F_{\mathrm{NUV}}$ in each of those categories is compared under the null hypothesis that they are the same.
%In this case, a non-parametric test could be preferred, such as a two-sample Kolmogorov-Smirnov test or perhaps a Mann-Whitney $U$ test.

\subsection{Constraining power for the origins of life as a function of biosignature location} % corresponds to conclusion points 2, 5
It comes to no surprise that the success rate of such a test is sensitive to the sample size of the survey and to the occurrence of life on temperate exoplanets.
As we have shown, the statistical power of this test also depends on the distribution of past \gls{NUV} fluxes in the sample and on the required threshold flux.
Optimizing the survey to sample a wide range of NUV flux values, particularly at the extremes, can enhance the likelihood of obtaining strong evidence for or against the hypothesis.
Intermediate values of the threshold \gls{NUV} flux are more likely to yield strong evidence than extreme values, as the dataset under the alternative hypothesis $H_1$ differs more from the null hypothesis in this case while still being sufficiently populated.
The required threshold flux is, of course, a priori unknown and we cannot influence it.
If, however, better theoretical predictions for the required \gls{NUV} flux for abiogenesis become available, the survey strategy can be further optimized, for instance by targeting planets that are estimated to have received a \gls{NUV} flux slightly below and above this threshold.

@@

\subsection{Contextual support for potential biosignature detections} % corresponds to ... which conclusion?
The predicted interplay of \gls{NUV} flux and \gls{HZ} occupancy in enabling abiogenesis via the cyanosulfidic scenario could in principle be used to add or remove credibility from a tentative biosignature detection.
For example, with a strong believe that this scenario is the only viable one for the origins of life, a biosignature detection on a planet orbiting a strongly UV-radiating star may add credibility to the detection.
Conversely, a biosignature detection on a planet estimated to have received very little UV~radiation would increase the likelihood of a false positive detection.
On the other hand, should the detection in the latter case be confirmed, it could be used to falsify the UV~hypothesis.
